Questions to Developers

### 2021-06-25 StateOfPractice/Ao-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
Update to medical image domain expert meeting

\bi
\item \structure{What experience do you, or your students, have with developing
    software?}
\item \structure{How big would the development group be?}
\item \structure{What is the typical background of a developer?}
\item \structure{How many users would you software typically have?}
\item \structure{What is the typical background of a user}
\item \structure{Currently, what are the most significant obstacles in your
    development process?}
\item \structure{How might you change your development process to remove or
    reduce these obstacles?}      
\ei

@@

\bi
\item \structure{How does documentation fit into your development process? Would improved
docu- mentation help with the obstacles you typically face?}
\item \structure{In the past, is there any major obstacle to your development process that
has been solved? How did you solve it?}
\item \structure{What is your software development model? For example, waterfall, agile,
etc.}
\item \structure{What is your project management process? Do you think improving this
process can tackle the current problem? Were any project management tools
used?}
\ei

@@

\bi
\item \structure{Was it hard to ensure the correctness of the software? If there were any obstacles, what methods
have been considered or practiced to improve the situation? If practiced, did it work?}
\item \structure{When designing the software, did you consider the ease of future changes? For example, will it be
hard to change the structure of the system, modules or code blocks? What measures have been taken
to ensure the ease of future changes and maintains?}
\item \structure{Provide instances where users have misunderstood the software. What, if any, actions were taken
to address understandability issues?}
\item \structure{What, if any, actions were taken to address usability issues?}
\ei

@@

\bi
\item \structure{Do you think the current documentation can clearly convey all necessary knowledge to the users?
If yes, how did you successfully achieve it? If no, what improvements are needed?}
\item \structure{Do you have any concern that your computational results won’t be reproducible in the future?
Have you taken any steps to ensure reproducibility?}
\ei

>>>>

\bi
\item \structure{What experience do you, or your students, have with developing
    software?}
\item \structure{How big would the development group be?}
\item \structure{What is the typical background of a developer?}
\item \structure{How many users would you software typically have?}
\item \structure{What is the typical background of a user?}
\item \structure{Currently, what are the most significant obstacles in your
    development process?}
\item \structure{How might you change your development process to remove or
    reduce these obstacles?}
\item \structure{How does documentation fit into your development process? Would improved
  documentation help with the obstacles you typically face?}      
\ei

@@

\begin{frame}
\frametitle{Developer Questions Continued}

\bi
\item \structure{In the past, is there any major obstacle to your development process that
  has been solved? How did you solve it?}
\item \structure{What is your software development model? For example, waterfall, agile,
  etc.}
\item \structure{What is your project management process? Do you think improving this
  process can tackle the current problem? Were any project management tools
  used?}
\item \structure{Was it hard to ensure the correctness of the software? If there
    were any obstacles, what methods have been considered or practiced to
    improve the situation? If practiced, did it work?}
\ei

@@

\begin{frame}
\frametitle{Developer Questions Continued}

\bi
\item \structure{When designing the software, did you consider the ease of
    future changes? For example, will it be hard to change the structure of
    the system, modules or code blocks? What measures have been taken to ensure
    the ease of future changes and maintainance?}
\item \structure{Provide instances where users have misunderstood the
    software. What, if any, actions were taken to address understandability
    issues?}
\item \structure{What, if any, actions were taken to address usability issues?}
\item \structure{Do you think the current documentation can clearly convey all
    necessary knowledge to the users? If yes, how did you successfully achieve
    it? If no, what improvements are needed?}
\ei

@@

\begin{frame}
\frametitle{Developer Questions Continued}

\bi
\item \structure{Do you have any concern that your computational results won't
    be reproducible in the future? Have you taken any steps to ensure
    reproducibility?}  \ei
